Supplementary Information: \nTree height, microhabitat, and hydraulic traits shape drought responses in a temperate broadleaf forest

### 2019-10-26 manuscript/climate_sensitivity_SI.Rmd
Updated file names and added bark regression

heights <- read.csv("tables_figures/height_regression.csv", stringsAsFactors = FALSE)
kable(heights, booktabs=TRUE, format = "latex", caption = "Species-specific height regression equations") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```

```{r, Table S2, eval=TRUE, echo=FALSE, message=FALSE}
tableS2 <- read.csv("tables_figures/candidate_traits.csv", stringsAsFactors = FALSE)
kable(tableS2, booktabs=TRUE, format = "latex", caption = "Candidate variables for best model") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```

```{r, Plot, echo=FALSE, out.width='100%', fig.cap = "Map of ForestGEO plot", fig.pos='ht'}
  knitr::include_graphics("tables_figures/ForestGEO_plot.jpg")
```

*how do we want to present Table S3? Would it be better as an image of an excel file, since it's so large? Did we want to keep all coefficients here?*
```{r, Table S3, eval=TRUE, echo=FALSE, message=FALSE}
tableS3 <- read.csv("tables_figures/top_models_dAIC.csv", stringsAsFactors = FALSE)
kable(tableS3, booktabs=TRUE, format = "latex", caption = "Top model variations for each drought scenario, with dAICc values <= 2") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```

![Location of cored trees](tables_figures/FigureS3.png){width=500px}

![Figure S1](tables_figures/FigureS1.png)
(see Issue #32)

>>>>

bark <- read.csv("tables_figures/tableS1_bark_regression.csv", stringsAsFactors = FALSE)
bark[,2] <- NULL
kable(bark, booktabs=TRUE, format = "latex", caption = "Species-specific bark thickness regression equations") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```

```{r, Table S2, eval=TRUE, echo=FALSE, message=FALSE}
library(knitr)
library(kableExtra)

heights <- read.csv("tables_figures/tableS2_height_regression.csv", stringsAsFactors = FALSE)
heights[,2] <- NULL
kable(heights, booktabs=TRUE, format = "latex", caption = "Species-specific height regression equations") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```

```{r, Table S3, eval=TRUE, echo=FALSE, message=FALSE}
tableS2 <- read.csv("tables_figures/tableS3_candidate_traits.csv", stringsAsFactors = FALSE)
kable(tableS2, booktabs=TRUE, format = "latex", caption = "Candidate variables for best model") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```

```{r Figure S1, echo=FALSE, out.width='100%', fig.cap = "Map of ForestGEO plot", fig.pos='ht'}
  knitr::include_graphics("tables_figures/figureS1_ForestGEO_plot.jpg")
```

*how do we want to present Table S3? Would it be better as an image of an excel file, since it's so large? Did we want to keep all coefficients here?*
```{r, Table S3, eval=TRUE, echo=FALSE, message=FALSE}
tableS3 <- read.csv("tables_figures/tableS3_top_models_dAIC.csv", stringsAsFactors = FALSE)
kable(tableS3, booktabs=TRUE, format = "latex", caption = "Top model variations for each drought scenario, with dAICc values <= 2") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```

![Location of cored trees](tables_figures/figureS2_location_cored_trees.png){width=500px}

![Figure S3](tables_figures/figureS3_traits_with_twi.png)
(see Issue #32)
